Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-12 Writing/CEA_2nd_round/replies_rev_2.rmd

---
title: "Reply to Reviewer #2"
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: word_template_format.docx
---

>>>>

---
title: "Reply to Reviewer #2"
output:
  bookdown::word_document2:
    fig_caption: yes
    number_sections: no
    global_numbering: true
    reference_docx: ../word_template_format.docx
---

### 2022-02-12 Writing/manuscript_cea.rmd

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = F,
  message = F,
  cache = TRUE,
  echo = F
)
```

@@

In this paper, we use the Causal Forest (CF) approach developed by @athey2016recursive and @Wager2018a to examine the accuracy of methods that estimate site-specific economically optimal N fertilizer rates (EONRs). We compare the EONR prediction performances of our CF-based approach to the widely used ML methods Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN), and we examine how yield prediction performance is related to EONR prediction performance, which allow us to examine whether model selection should be based on yield prediction accuracy when the ultimate goal is EOIR identifying. We use Monte Carlo simulations in which we synthetically generate yield and soil/field characteristics datasets to create stylized "field." Because real-world "true" EOIRs are unobservable, real-world data cannot be used to test the accuracy of statistical methods estimating EOIRs. This important difference contrasts starkly with yield prediction, since actual yields can be ground-truthed.

@@

Identity \@ref(eq:eqn2) states that the necessary elements of the information needed for profit maximization are the input price, the output price, and the partial derivative of the yield function with respect to the input. While knowledge of the yield function $f(I, \mathbf{c})$ in Eq. \@ref(eq:eqn1)) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the "change" in yield in response to a change in input rate is.

Recent papers using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21) and then derive changes in yield associated with changes in input rate to estimate site-specific input recommendations. On the other hand, Causal Forest is designed specifically to estimate a discrete version of Eq. \@ref(eq:eqn2) directly, examining the discrete changes in yield that result from discrete *changes* in the input application rate $I$, bypassing the estimation of $f(I, \mathbf{c})$. It may be suspected that CF will outperform other ML methods that identify EOIR indirectly through yield prediction. We now details how CF works below and why CF may perform better in predicting EOIR than other prediction-oriented ML methods used in the previous studies.

@@

Monte Carlo simulations were conducted for nitrogen experiments for corn production to estimate site-specific EONRs. The simulations' first step generated one thousand synthetic fields that "resembled" an actual field. Field characteristics and yield were simulated assuming the Mitscherlich-Baule (MB) yield response function. We used the RF, BRF, and CNN ML methods to estimate yield response functions, and we used the CF method to estimate treatment effects. For each method, we estimated site-specific EONRs using the training data set, and checked the statistical performance of the predicted site-specific EONR using the validation data set. Detailed descriptions of these steps are provided below. The *R* and *python* codes that implement the simulation analyses are available at https://github.com/tmieno2/ML_VRA.git.

@@

The first term on the right-hand side of Eq. \@ref(eq:eqn6) is the deterministic yield component. The variable $N$ represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot. Also in Eq. \@ref(eq:eqn6), $\alpha$, $\beta$, and $ymax$ are spatially varying parameters that govern how yield level is determined in conjunction with the applied N rate. They reflect local cell-level production conditions, such as soil characteristics and topography. For example, $\alpha$, which represents what the yield would be when no nitrogen is applied in conjunction with $ymax$, may reflect soil organic matter and residual nitrogen from previous year's production. $ymax$, which determines the maximum yield attainable, may include other micro nutrients like phosphorus, soil depth among others. $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen]. The error term of the yield $\varepsilon$ represents the composite of all the unobserved factors that affect crop yield beyond $\alpha$, $\beta$, $ymax$ and $N$. Each cell $(i,j)$'s "true" optimal N application rate, denoted $N^{opt}_{i,j}$, was calculated by solving a profit maximization problem by cell assuming that the prices of corn and N fertilizer were $\$0.138/kg$ and $\$1.323/kg$, respectively. These prices are used consistently for our simualtions. See Appendix \@ref(par-gen) for further details on how the paremeters were generated and sample maps of the parameters and true economically optimal N rates.

@@

In each simulation round, five field-trial N rates were determined based on the range of the round's cell-specific EONRs. 
Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percent quantile of the round's cell-specific EONRs. Then, the five trial design rates were $N_1 = Q_{0.05} - 20$, $N_5 = Q_{0.95} + 20$, $N_2 = N_1 + 0.25(N_5 - N_1)$, $N_3 = N_1 + 0.50(N_5 - N_1)$, $N_4 = N_1 + 0.75(N_5 - N_1)$. 
In each round, a Latin square design was followed to assign each plot one of the five N rates so established. The left-most panel of Figure \@ref(fig:fig-nExp-yield) shows an example of a trial design. The N rate was orthogonal to the error term in every simulation's example of trial design. This is important because if they were correlated, bias in the estimation of the impact of N on yield would be introduced into all of the ML methods. Since the treatment effect at each leaf is obtained simply by taking the difference of the average value of the dependent variable between the control and treated group within the leaf, CF requires the exogeneity of the treatment conditional on the independent variables to estimate the treatment effect consistently. Note that the violation of this condition would lead to biased estimation using the CF and the other ML methods.

@@

```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "An example of experimental design of N and generated yield at the subplot resolution"}

# (field_Ndesign + ggtitle("(a) Trial Design")) |
#   (vis_yield_subplot + ggtitle("(b) Simulated Yield Level"))
field_Ndesign | vis_yield_subplot
```

@@

In the third scenario, denoted "aabbyy," the researcher's data set did not contain values of $\alpha_{i}$, $\beta_{i}$, or $ymax_{i}$. Rather, it contained subplot-level values of permutations of $\alpha$, $\beta$, and $ymax$. Each of the three parameters were split into two parts in a spatially correlated manner, and six new covariates were created (see Appendix \@ref(split-pars) for the details about this prameter splitting process). These were $\alpha^{1}_{i}$, $\alpha^{2}_{i}$, $\beta^{1}_{i}$, $\beta^{2}_{i}$, $ymax^{1}_{i}$, and $ymax^{2}_{i}$. The two splitted variables were spatially correlated to reflect that many of the soil/field characteristics used to analyze OFPE data are spatially correlated. The values of $\alpha_{i}$, $\beta_{i}$ and $ymax_{i}$ did not indicate specific soil or field characteristics, but were functions of such. In reality, scientists cannot directly observe variables that can accurately predict yield plateau level, soil N content and N uptake efficiency. Rather, they use multiple observed soil/field characteristics to explain such phenological phenomena. For example, instead of using $ymax_{i}$ directly, some topographical land features and soil properties such as elevation and soil sand content could be used as yield-limiting factors [@jiang2004effect; @kravchenko2000correlation]. In reality, scientists may include more than three variables as covariates. This scenario should reduce the accuracy of EONR modeling for all the models compared to the ideal case.

@@

The RF, BRF, and CNN methods all followed the same conceptual steps to estimate site-specific EONR: 1) estimate the yield production functions and 2) calculate site-specific EONRs based on that estimated function. For the given modeling scenario, RF and BRF predict yield by using all the available covariates as explanatory variables in the estimation process. The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for RF and BRF modeling. RF ann BRF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving honest tree-building process), and the optimal values for these parameters were selected by cross-validation. Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same data set was used. To reduce the variance of predictions for prediction accuracy, we set the number of trees (*num.trees*) at a high value, $4000$.

@@

Since the CF-base approach always estimates the treatment effects using the lowest treatment rate $N_1$, the predicted treatment effects already represent differences in yields the from yield at $N_1$:

@@

For evaluation of yield and EONR predictions, a dataset from a different simulation round was used as the test dataset. For example, for simulation number 1, train dataset from simulation number 2 was used as the test dataset. This process works because the train datasets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$). Furtehr, each of the "train" datasets are generated independet of one another. Thefore, for a particular simulation round, the dataset in any of the other simualtion rounds can serve as a valid test dataset. This practice avoid creating another set of 1000 simulations fields unnecessarily.

The accuracy of EONR estimation was judged based on RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level. Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) we calculated relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N^{opt}_{i}$. For RF, BRF, and CNN, the accuracy of yield prediction was judged based on the RMSE ($kg/ha$) of the yield prediction against the true yields at the subplot level.

@@

## Comparison of EONR estimation accuracy

@@

Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML methods and modeling scenarios, respectively (CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always take $62.8$ kg/ha and \$$58.99$/ha, respectively). The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios. 
Interestingly, RF seems particularly vulnerable to the inclusion of more variables, with RMSE ($\hat{\pi}_{def}$) increasing from `r table_optN_prep[Model=="aby",rmse_optN_RF]` (`r table_optN_prep[Model=="aby", pi_loss_RF]`) in the "aby" scenario to `r table_optN_prep[Model=="aabbyytt", rmse_optN_RF]` (`r table_optN_prep[Model=="aabbyytt", pi_loss_RF]`) in the "aabbyytt" scenario. CF-base was more robust to the inclusion of additional variables. Overall, the simulations present CF-base as the clear winner in estimating EONR.

@@

Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions. It plots the estimated treatment effects against true treatment effects by treatment types and ML methods (RF, BRF, and CF-base) under the "aabbyytt" scenario in one of the one thousand simulations rounds. The figure shows points clustered around the red 1-to-1 line, meaning that the estimated treatment effects did not exhibit significant bias. However, the models differed substantially in the accuracy of their treatment effect estimations. Points are clustered more tightly about the 1-to-1 line for CF-base than RF and BRF. That is, CF-base estimated treatment effects much more efficiently than did RF and BRF, which focus on yield prediction rather than treatment effect estimation.

@@

## The relationship between yield and EONR prediction performances.

@@

```{r plot-y-optN, fig.width=7, fig.height=7.5, fig.cap = "The relationship in the performance between EONR estimation and yield prediction by ML method and modeling scenario"}
fig_y_optN
```

@@

All previous research has followed a two-step procedure to estimate site-specific EONRs. The first step was to select the model that predicts yield most accurately, and the following step used the selected model to predict EONR. Table \@ref(tab:count-table) shows that following this process led to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds. For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of $1000$ iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations. That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF models best at yield prediction did not provide EONR estimates that led to high profits. Similarly, in no cased did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously. For example, Table \@ref(tab:count-table) shows that BRF predicted yield best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best. But, BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.

@@

```{r count-table, tab.cap = "Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances for prediction-oriented ML methods"}
report_summary_res_CNN_RF_BRF
```

@@

ML methods are appealing tools that can potentially improve site-specific input rate management by capturing heterogeneous treatment effects introduced by complex non-linear and multidimensional interactions of soil and field characteristics. Many kinds of prediction-oriented ML methods have been used for this purpose. We have introduced the use of CF, a relatively new method, which, unlike prediction-oriented ML methods, focuses on the identification of heterogeneous causal effects of treatment.

We examined the use of CF for site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF. It is recommended that BRF is used in place of RF according to out results. Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.

We also showed that the model's yield prediction accuracy has little to do with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the ultimate goal of the experiment is to create a site-specific EOIR map. Many studies seek to predict yield level accurately using deep learning methods. However, the usefulness of such models may be questionable when it comes to using them for making management decisions. Further examinations into this issues is warranted.

# Acknowledgement

>>>>

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = F,
  message = F,
  cache = T,
  echo = F
)
```

@@

In this paper, we use the Causal Forest (CF) approach developed by @athey2016recursive and @Wager2018a to examine the accuracy of methods that estimate site-specific economically optimal N fertilizer rates (EONRs). We compare the EONR prediction performances of our CF-based approach to the widely used ML methods Random Forest (RF), Boosted Random Forest (BRF), and Convolutional Neural Network (CNN), and we examine how yield prediction performance is related to EONR prediction performance, which allow us to examine whether model selection should be based on yield prediction accuracy when the ultimate goal is EOIR identification. We use Monte Carlo simulations in which we synthetically generate yield and soil/field characteristics datasets to create stylized "field." Because real-world "true" EOIRs are unobservable, real-world data cannot be used to test the accuracy of statistical methods estimating EOIRs. This important difference contrasts starkly with yield prediction, since actual yields can be ground-truthed.

@@

Identity \@ref(eq:eqn2) states that the necessary elements of the information needed for profit maximization are the input price, the output price, and the partial derivative of the yield function with respect to the input. While knowledge of the yield function $f(I, \mathbf{c})$ in Eq. \@ref(eq:eqn1) is sufficient to solve the maximization problem above (since its derivative can be calculated), identity \@ref(eq:eqn2) shows that it is not a necessary condition; rather, knowing the "change" in yield in response to a change in input rate is.

Recent studies using ML methods to estimate the effectiveness of various agricultural input management strategies first estimate yield function, $f(I, \mathbf{c})$ (e.g., @krause2020random; @barbosa2020modeling; @Gardner21) and then derive changes in yield associated with changes in input rate to estimate site-specific input recommendations. On the other hand, Causal Forest is designed specifically to estimate a discrete version of Eq. \@ref(eq:eqn2) directly, examining the discrete changes in yield that result from discrete *changes* in the input application rate $I$, bypassing the estimation of $f(I, \mathbf{c})$. It may be suspected that CF will outperform other ML methods that identify EOIR indirectly through yield prediction. We now details how CF works below and why CF may perform better in predicting EOIR than other prediction-oriented ML methods used in the previous studies.

@@

Monte Carlo simulations were conducted for nitrogen experiments for corn production to estimate site-specific EONRs. The simulations' first step generated one thousand synthetic fields that "resembled" an actual field. Field characteristics and yield were simulated assuming the Mitscherlich-Baule (MB) yield response function. We used the RF, BRF, and CNN ML methods to estimate yield response functions, and we used the CF method to estimate treatment effects. For each method, we estimated site-specific EONRs using the training data set, and checked the statistical performance of the predicted site-specific EONR using the validation data set. Detailed descriptions of these steps are provided below. The *R* and *python* codes that implement the simulation analyses are available at @Kakimoto2022codes.

@@

The first term on the right-hand side of Eq. \@ref(eq:eqn6) is the deterministic yield component. The variable $N$ represents the nitrogen fertilizer application rate (kg/ha) which the trial designs varied by plot. Also in Eq. \@ref(eq:eqn6), $\alpha$, $\beta$, and $ymax$ are spatially varying parameters that govern how yield level is determined in conjunction with the applied N rate. They reflect local cell-level production conditions, such as soil characteristics and topography. For example, $\alpha$, which represents what the yield would be when no nitrogen is applied in conjunction with $ymax$, may reflect soil organic matter and residual nitrogen from previous year's production. $ymax$, which determines the maximum yield attainable, may include other micro nutrients like phosphorus and soil depth. $\beta$ can be interpreted as reflecting how efficiently the crop uses N to create grain mass, and might depend on soil properties that affect the availability of applied N fertilizer to the crop, say due to N immobilization, leaching, denitrification, and volatilization [@johnson2005nitrogen; @alva2006nitrogen]. The error term of the yield $\varepsilon$ represents the composite of all the unobserved factors that affect crop yield beyond $\alpha$, $\beta$, $ymax$ and $N$. Each cell $(i,j)$'s "true" optimal N application rate, denoted $N^{opt}_{i,j}$, was calculated by solving a profit maximization problem by cell assuming that the prices of corn and N fertilizer were $\$0.138/kg$ and $\$1.323/kg$, respectively. These prices are used consistently for our simualtions. See Appendix \@ref(par-gen) for further details on how the paremeters were generated and sample maps of the parameters and true economically optimal N rates.

@@

In each simulation round, five field-trial N rates were determined based on the range of the round's cell-specific EONRs. 
Let $Q_q$ ($q \in [0,1]$) denote the $100 \times q$ percent quantile of the round's cell-specific EONRs. Then, the five trial design rates were $N_1 = Q_{0.05} - 20$, $N_5 = Q_{0.95} + 20$, $N_2 = N_1 + 0.25(N_5 - N_1)$, $N_3 = N_1 + 0.50(N_5 - N_1)$, $N_4 = N_1 + 0.75(N_5 - N_1)$. 
In each round, a Latin square design was followed to assign each plot one of the five N rates so established. The left-most panel of Figure \@ref(fig:fig-nExp-yield) shows an example of a trial design. The N rate was orthogonal to the error term in every simulation's example of trial design. This is important because if they were correlated, bias in the estimation of the impact of N on yield would be introduced into all the ML methods. Since the treatment effect at each leaf is obtained simply by taking the difference of the average value of the dependent variable between the control and treated group within the leaf, CF requires the exogeneity of the treatment conditional on the independent variables to estimate the treatment effect consistently. Note that the violation of this condition would lead to biased estimation using the CF and the other ML methods.

@@

```{r fig-nExp-yield, fig.width=7, fig.height=6, fig.cap = "An example of experimental design of N and generated yield at the subplot resolution"}
field_Ndesign | vis_yield_subplot
```

@@

In the third scenario, denoted "aabbyy," the researcher's data set did not contain values of $\alpha_{i}$, $\beta_{i}$, or $ymax_{i}$. Rather, it contained subplot-level values of permutations of $\alpha$, $\beta$, and $ymax$. Each of the three parameters were split into two parts in a spatially correlated manner, and six new covariates were created (see Appendix \@ref(split-pars) for the details about this parameter-splitting process). These were $\alpha^{1}_{i}$, $\alpha^{2}_{i}$, $\beta^{1}_{i}$, $\beta^{2}_{i}$, $ymax^{1}_{i}$, and $ymax^{2}_{i}$. The two split variables were spatially correlated to reflect that many of the soil/field characteristics used to analyze OFPE data are spatially correlated. The values of $\alpha_{i}$, $\beta_{i}$ and $ymax_{i}$ did not indicate specific soil or field characteristics, but were functions of such. In reality, scientists cannot directly observe variables that can accurately predict yield plateau level, soil N content and N uptake efficiency. Rather, they use multiple observed soil/field characteristics to explain such phenological phenomena. For example, instead of using $ymax_{i}$ directly, some topographical land features and soil properties such as elevation and soil sand content could be used as yield-limiting factors [@jiang2004effect; @kravchenko2000correlation]. In reality, scientists may include more than three variables as covariates. This scenario should reduce the accuracy of EONR modeling for all the models compared to the ideal case.

@@

The RF, BRF, and CNN methods all followed the same conceptual steps to estimate site-specific EONR: 1) estimate the yield production functions and 2) calculate site-specific EONRs based on that estimated function. For the given modeling scenario, RF and BRF predict yield by using all the available covariates as explanatory variables in the estimation process. The `grf` package (version 1.2.0 [@tibshirani2018package]) in R was used for RF and BRF modeling. RF ann BRF from the `grf` package have several tunable hyperparameters (e.g., the minimum node size in each tree, the number of covariates used for node splitting, and parameters involving an honest tree-building process), and the optimal values for these parameters were selected by cross-validation. Individual trees in a forest were built with randomly subsampled observations, leading to a different prediction in every forest even when the same data set was used. To reduce the variance of predictions for prediction accuracy, we set the number of trees (*num.trees*) at a high value, $4000$.

@@

Since the CF-base approach always estimates the treatment effects using the lowest treatment rate $N_1$, the predicted treatment effects already represent differences in yields from yield at $N_1$:

@@

For evaluation of yield and EONR predictions, a data set from a different simulation round was used as the test data set. For example, for simulation number 1, the training data set from simulation number 2 was used as the test data set. This process works because the training data sets were generated by the same data generating process, yet have different underlying field parameters ($\alpha$, $\beta$, $ymax$). Further, all training data sets were generated independently, so for any particular simulation round, the data set from any other round could serve as a valid test data set. This practice made the creation of one thousand additional simulations fields unnecessary.

The accuracy of EONR estimation was judged based on RMSE ($kg/ha$) of the EONR estimation against the true EONR at the subplot level. Using the EONR estimates, we also calculated profit-deficits ($\$/ha$) (i.e., $\hat{\pi}_{def}$) relative to the true maximum profit at the subplot level, defined as profit under the true yield response functions evaluated at $N^{opt}_{i}$. For RF, BRF, and CNN, the accuracy of yield prediction was judged based on the RMSE ($kg/ha$) of the yield prediction against the true yields at the subplot level.

@@

## Comparison of EONR Estimation Accuracy

@@

Figure \@ref(fig:dist-optN) and Figure \@ref(fig:dist-piLoss) show the distributions of the one thousand RMSEs of the EONR estimations and $\hat{\pi}_{def}$ by ML methods and modeling scenarios, respectively (CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always took values $62.8$ kg/ha and \$$58.99$/ha, respectively.) The center of distribution mass of the CF-base's RMSE values and $\hat{\pi}_{def}$ are to the left of the centers of the distribution masses of the other methods' RMSE values, showing that CF-base more accurately and consistently estimated EONR across all the modeling scenarios. 
Interestingly, RF seems particularly vulnerable to the inclusion of more variables, with RMSE ($\hat{\pi}_{def}$) increasing from `r table_optN_prep[Model=="aby",rmse_optN_RF]` (`r table_optN_prep[Model=="aby", pi_loss_RF]`) in the "aby" scenario to `r table_optN_prep[Model=="aabbyytt", rmse_optN_RF]` (`r table_optN_prep[Model=="aabbyytt", pi_loss_RF]`) in the "aabbyytt" scenario. CF-base was more robust to the inclusion of additional variables. Overall, the simulations present CF-base as the clear winner in estimating EONR.

@@

Figure \@ref(fig:plot-tre) illustrates the underlying cause of CF-base's superior EONR predictions. It plots the estimated treatment effects against true treatment effects by treatment types and ML methods under the "aabbyytt" scenario in one of the one thousand simulations rounds. The figure shows points clustered around the red 1-to-1 line, meaning that the estimated treatment effects did not exhibit significant bias. However, the models differed substantially in the accuracy of their treatment effect estimations. Points are clustered more tightly about the 1-to-1 line for CF-base than RF and BRF. That is, CF-base estimated treatment effects much more efficiently than did RF and BRF, which focus on yield prediction rather than treatment effect estimation.

@@

## The Relationship between Yield and EONR Prediction Performances.

@@

```{r plot-y-optN, fig.width=7, fig.height=7.5, fig.cap = "The relationship in the performance between EONR estimation and yield prediction, by ML method and modeling scenario"}
fig_y_optN
```

@@

All previous research has followed a two-step procedure to estimate site-specific EONRs. The first step was to select the model that predicts yield most accurately, and the following step used the selected model to predict EONR. Table \@ref(tab:count-table) shows that following this process led to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds. For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of $1000$ iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations. That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF models best at yield prediction did not provide EONR estimates that led to high profits. Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously. For example, Table \@ref(tab:count-table) shows that BRF predicted yield best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best. But BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.

@@

```{r count-table, tab.cap = "Relationship between the EONR prediction performances (as measured by profit) and the yield prediction performances of prediction-oriented ML methods"}
report_summary_res_CNN_RF_BRF
```

@@

ML methods are appealing tools that can potentially improve site-specific input rate management by capturing heterogeneous treatment effects introduced by complex non-linear and multidimensional interactions of soil and field characteristics. Several kinds of prediction-oriented ML methods have been used for this purpose. We have introduced the use of CF, a relatively new method, which, unlike prediction-oriented ML methods, focuses on the identification of heterogeneous causal effects of treatment.

We examined the use of CF in the generation of site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF.  Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.

We also showed that the model's yield prediction accuracy has little to do with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map. Many studies seek to predict yield level accurately using deep learning methods. Our results question usefulness of such models in the making of management decisions. Further examinations into these issues are warranted.

# Acknowledgements
